INTELLIGENT SYSTEMS

### 2021-04-05 slides.tex
finish slide paper4

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Chromaticity}
    \begin{block}{Chromatic adaptation - \href{https://en.wikipedia.org/wiki/Color_vision}{\underline{Wikipedia}}}
        \emph{"In color vision, chromatic adaptation refers to color constancy; the 
        ability of the visual system to preserve the appearance of an object under 
        a wide range of light sources."}
    \end{block}
    The only information available on the light source are: the "\emph{Spectral 
    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
    Thanks to this information, we can obtain the existing chromaticity in the image 
    and compare it with that obtained from the "\emph{Camera Spectral Senstivities}" (CSS).
    \begin{block}{Target}
        The goal is to be able to bring the white point, calculated by each 
        algorithm, closer to the white point of the ground truth, within the same 
        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CMM) 
        is used.
    \end{block}
\end{frame}

@@

>>>>

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Chromaticity}
    \begin{block}{Chromatic adaptation - \href{https://en.wikipedia.org/wiki/Color_vision}{\underline{Wikipedia}}}
        \emph{"In color vision, chromatic adaptation refers to color constancy; the 
        ability of the visual system to preserve the appearance of an object under 
        a wide range of light sources."}
    \end{block}
    The only information available on the light source are: the "\emph{Spectral 
    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
    Thanks to this information, we can obtain the existing chromaticity in the image 
    and compare it with that obtained from the "\emph{Camera Spectral Senstivities}" (CSS).
    \begin{block}{Target}
        The goal is to be able to bring the white point, calculated by each 
        algorithm, closer to the white point of the ground truth, within the same 
        color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CCM) 
        is used.
    \end{block}
\end{frame}

@@

\begin{frame}{EXPERIMENTAL RESULTS - Supervised methods}
    Color constancy can also be calculated from convolutional neural networks (\emph{CCNs}) such as the one proposed in \footfullcite{0807099125}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper4/25tech1.png}
        \centering
        \caption{Camera Independence with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec1}
    \end{figure}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
                \caption{\small Camera Independence on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width=0.8\linewidth]{images/paper4/25tech3.png}
                \caption{\small Camera Independence on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{CONCLUSION}
    The dataset proposed in this paper is useful for testing the behavior of 
    an algorithm, or a model based on CNN, in the search of camera/scene-independece. 
    Achieving this goal can also be done using a CNN if the CMM process is 
    applied to its input set. It is necessary to specify that, in order to 
    achieve the final result, it is essential to have the spectral sensitivities of each camera 
    without which it would not be possible to achieve camera independence.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.5 \linewidth]{images/paper4/CSS.png}
        \centering
        \caption{Camera Spectral Sensitivities (CSS) of the light sources.}
        \label{fig:CNNtec1}
    \end{figure}
\end{frame}
